---
title: "Data Appendix"
author: "Mine Cetinkaya-Rundel"
date: "February 12, 2016"
output: html_document
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # don't show code chunks in output
```

```{r load-packages, message = FALSE}
# load packages
library(dplyr)
library(ggplot2)
library(mosaic)
```

## Load data

```{r load-data, echo = TRUE}
load("oww.RData")
```

## Data Dictionary

**Note:** The data dictionary is not yet complete, but there should be sufficient
information here to give you an idea of how to create such a document.

- `year` - year
    + original variable name: `y0`
    
```{r summary-year}
favstats(data = oww, year)
```

```{r hist-year, message = FALSE, fig.height = 3, fig.width = 7}
ggplot(data = oww, aes(x = year)) +
  geom_histogram(binwidth = 5)
```

- `country_ILO` - country code (from ILO October Inquiry)
    + original variable name: `y1`
    
```{r summary-country_ILO}
oww %>%
  group_by(country_ILO) %>%
  summarise(n())
```

```{r hist-country_ILO, message = FALSE, fig.height = 3, fig.width = 15}
ggplot(data = oww, aes(x = country_ILO)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

- `country_WDI` - country code (from World Development Indicators)
    + original variable name: `country`
    
```{r summary-country_WDI}
oww %>%
  group_by(country_WDI) %>%
  summarise(n())
```

```{r hist-country_WDI, message = FALSE, fig.height = 3, fig.width = 15}
ggplot(data = oww, aes(x = country_WDI)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```    

- `industry` - industry code (from ILO October Inquiry)
    + original variable name: `y3`

```{r summary-industry}
oww %>%
  group_by(industry) %>%
  summarise(n())
```

```{r hist-industry, message = FALSE, fig.height = 3, fig.width = 15}
ggplot(data = oww, aes(x = industry)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```    
  
- `occupation` - occupation code (from ILO October Inquiry)
    + original variable name: `y4`

```{r summary-occupation}
oww %>%
  group_by(occupation) %>%
  summarise(n())
```

```{r hist-occupation, message = FALSE, fig.height = 3, fig.width = 15}
ggplot(data = oww, aes(x = occupation)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
``` 
    
- `hw1` - hourly: standard data LCU

```{r summary-hw1}
favstats(data = oww, hw1)
```

```{r hist-hw1, message = FALSE, fig.height = 3, fig.width = 7}
ggplot(data = oww, aes(x = hw1)) +
  geom_histogram()
```

- `hw2wu` - hourly: country-specific calibration (uni) LCU

```{r summary-hw2wu}
favstats(data = oww, hw2wu)
```

```{r hist-hw2wu, message = FALSE, fig.height = 3, fig.width = 7}
ggplot(data = oww, aes(x = hw2wu)) +
  geom_histogram()
```

- `hw3wu` - hourly: country-specific calibration with imputation (uni) LCU

```{r summary-hw3wu}
favstats(data = oww, hw3wu)
```

```{r hist-hw3wu, message = FALSE, fig.height = 3, fig.width = 7}
ggplot(data = oww, aes(x = hw3wu)) +
  geom_histogram()
```

- `hw4wu` - hourly: uniform calibration (uni) LCU

```{r summary-hw4wu}
favstats(data = oww, hw4wu)
```

```{r hist-hw4wu, message = FALSE, fig.height = 3, fig.width = 7}
ggplot(data = oww, aes(x = hw4wu)) +
  geom_histogram()
```

- `hw2wl` - hourly: country-specific calibration (lex) LCU

```{r summary-hw2wl}
favstats(data = oww, hw2wl)
```

```{r hist-hw2wl, message = FALSE, fig.height = 3, fig.width = 7}
ggplot(data = oww, aes(x = hw2wl)) +
  geom_histogram()
```

- `hw3wl` - hourly: country-specific calibration with imputation (lex) LCU

```{r summary-hw3wl}
favstats(data = oww, hw3wl)
```

```{r hist-hw3wl, message = FALSE, fig.height = 3, fig.width = 7}
ggplot(data = oww, aes(x = hw3wl)) +
  geom_histogram()
```

- `hw4wl` - hourly: uniform calibration (lex) LCU
- `hw1us` - hourly: standard data US$
- `hw2wuus` - hourly: country-specific calibration (uni) US$
- `hw3wuus` - hourly: country-specific calibration with imputation (uni) US$
- `hw4wuus` - hourly: uniform calibration (uni) US$
- `hw2wlus` - hourly: country-specific calibration (lex) US$
- `hw3wlus` - hourly: country-specific calibration with imputation (lex) US$ 
- `hw4wlus` - hourly: uniform calibration (lex) US$
- `mw1` - monthly: standard data LCU 
- `mw2wu` - monthly: country-specific calibration (uni) LCU
- `mw3wu` - monthly: country-specific calibration with imputation (uni) LCU
- `mw4wu` - monthly: uniform calibration (uni) LCU 
- `mw2wl` - monthly: country-specific calibration (lex) LCU 
- `mw3wl` - monthly: country-specific calibration with imputation (lex) LCU 
- `mw4wl` - monthly: uniform calibration (lex) LCU 
- `mw1us` - monthly: standard data US$
- `mw2wuus` - monthly: country-specific calibration (uni) US$
- `mw3wuus` - monthly: country-specific calibration with imputation (uni) US$
- `mw4wuus` - monthly: uniform calibration (uni) US$
- `mw2wlus` - monthly: country-specific calibration (lex) US$
- `mw3wlus` - monthly: country-specific calibration with imputation (lex) US$
- `mw4wlus` - monthly: uniform calibration (lex) US$
- `curr` - currency as reported in ILO October Inquiry
- `exrt` - exchange rate: LCU per US$
- `conv`- conversion factor for wages in LCU
- `curr_conv` - currency used for conversion factor
